Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry

### 2017-04-14 pre_post_biorxiv.tex
Working PDF of submitting and biorXiv versions

% title goes here:
\begin{flushleft}
{\LARGE
\textbf\newline{Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry}
}
\newline
% authors go here:
\\
A. Bradley Duthie\textsuperscript{1,*},
Greta Bocedi\textsuperscript{1},
Ryan R. Germain\textsuperscript{1},
Matthew E. Wolak\textsuperscript{1},
Jane M. Reid\textsuperscript{1}
\\
\bigskip
\bf{1} Institute of Biological and Environmental Sciences, School of Biological Sciences, Zoology Building, Tillydrone Avenue, University of Aberdeen, Aberdeen AB24 2TZ, United Kingdom
%\\
%\bf{2} Affiliation B
\\
\bigskip
*  alexander.duthie@stir.ac.uk, brad.duthie@gmail.com

@@

{\color{Gray}
    \begin{adjustwidth}{-2.2in}{0in}
    \mysidecaption{0.32}
{ 
        \begin{justify}
        \vspace{-0.25 mm}
        \captionof{figures/poly_costs.pdf}
        {\bf Figure 1:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fixed to zero (i.e., random fertilisation) or (B, D, F, and H) allowed to evolve freely. Costs of polyandry ($c_p$) increase across rows from zero (A and B) to 0.01 (G and H). Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations. Negative mean allele values indicate inbreeding avoidance or tendency for monandry, and positive values indicate inbreeding preference or tendency for polyandry. Dotted lines demarcate mean allele values of zero. 
    \end{justify}{\t}
}[t]
{
   \includegraphics[height=18cm]{figures/poly_costs.pdf}%
}
    \end{adjustwidth}
}

@@

%{\color{Gray}
%\begin{adjustwidth}{-2.2in}{0in}
%\mysidecaption{0.68}
%{%
%   \includegraphics[height=10.25cm]{figures/Pp_vals.png}%
%}%
%{%
%   \captionof{figures/Pp_vals.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 2:} Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with default parameter values and zero costs. Red lines in (A) and (C) show mean polyandry allele values across all individuals in a single simulation over 40000 generations. Positive and negative allele values contribute to polyandry and monandry, respectively. In the final generation, mean allele value was below (A) or above (C) zero (demarcated by the dotted line). Nevertheless, due to the threshold nature of expression of the polygenic polyandry phenotype, polyandry and monandry are expressed in both populations. Histograms in (B) and (D) show females' tendency for polyandry phenotypes in the final generation; white and grey shading indicates monandrous and polyandrous females, respectively. Arrows and numbers indicate mean phenotype values. Because each trait includes 10 diploid loci with additive effects, phenotype values are ca 20 times allele values. \end{justify}{\t}%
%}[t]
%\end{adjustwidth}
%}

@@

%{\color{Gray}
%\begin{adjustwidth}{-2.2in}{0in}
%\mysidecaption{0.31}
%{%
%   \captionof{figures/rel_costs.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 3:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve. Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations. Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry. In all panels, polyandry is cost free. \end{justify}{\t}%
%}
%{%
%   \includegraphics[height=14cm]{figures/rel_costs.png}%
%}%
%[t]
%\end{adjustwidth}
%}

@@

@@

\begin{small}
\bibliography{ms_pre_post}
\bibliographystyle{amnatnat}
\end{small}

>>>>

% title goes here:
\begin{flushleft}
{\LARGE
\textbf\newline{Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry}
}
\newline
% authors go here:
\\
A. Bradley Duthie\textsuperscript{1,*}, [...],
%Greta Bocedi\textsuperscript{1},
%Ryan R. Germain\textsuperscript{1},
%Matthew E. Wolak\textsuperscript{1},
Jane M. Reid\textsuperscript{2}
\\
\bigskip
\begin{small}
\bf{1.} Biological and Environmental Sciences, University of Stirling, Stirling FK9 4LA, United Kingdom \\
\bf{2.} Institute of Biological and Environmental Sciences, University of Aberdeen, Aberdeen AB24 2TZ, United Kingdom
\end{small}
%\\
%\bf{2} Affiliation B
\\
\bigskip
*  alexander.duthie@stir.ac.uk, brad.duthie@gmail.com

@@

{\color{Gray}
    \begin{adjustwidth}{-2.2in}{0in}
    \mysidecaption{0.275}
{ 
        \begin{justify}
        \vspace{-14.25 mm}
        \captionof{figures/poly_costs.pdf}
        {\bf Figure 1:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fixed to zero (i.e., random fertilisation) or (B, D, F, and H) allowed to evolve freely. Costs of polyandry ($c_p$) increase across rows from zero (A and B) to 0.01 (G and H). Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations. Negative mean allele values indicate inbreeding avoidance or tendency for monandry, and positive values indicate inbreeding preference or tendency for polyandry. Dotted lines demarcate mean allele values of zero.
    \end{justify}{\t}
}
{
   \includegraphics[height=18cm]{figures/poly_costs.pdf}%
}
    \end{adjustwidth}
}

@@

{\color{Gray}
\begin{adjustwidth}{-2.2in}{0in}
\mysidecaption{0.70}
{
   \includegraphics[height=10.25cm]{figures/Pp_vals.pdf}%
}
{%
   \captionof{figures/Pp_vals.png}\begin{justify}\vspace{0.75 mm} \textbf{Figure 2:} Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with default parameter values and zero costs. Red lines in (A) and (C) show mean polyandry allele values across all individuals in a single simulation over 40000 generations. Positive and negative allele values contribute to polyandry and monandry, respectively. In the final generation, mean allele value was below (A) or above (C) zero (demarcated by the dotted line). Nevertheless, due to the threshold nature of expression of the polygenic polyandry phenotype, polyandry and monandry are expressed in both populations. Histograms in (B) and (D) show females' tendency for polyandry phenotypes in the final generation; white and grey shading indicates monandrous and polyandrous females, respectively. Arrows and numbers indicate mean phenotype values. Because each trait includes 10 diploid loci with additive effects, phenotype values are ca 20 times allele values.  \end{justify}{\t}%
}
\end{adjustwidth}
}

@@

{\color{Gray}
\begin{adjustwidth}{-2.2in}{0in}
\mysidecaption{0.275}
{%
   \captionof{figures/rel_costs.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 3:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve. Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations. Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry. In all panels, polyandry is cost free. \end{justify}{\t}%
}
{%
   \includegraphics[height=13.5cm]{figures/rel_costs.pdf}%
}%
\end{adjustwidth}
}

@@

{\color{Gray}
\begin{adjustwidth}{-2.2in}{0in}
\mysidecaption{0.70}
{%
   \includegraphics[height=13.5cm]{figures/fixed_adapt.pdf}%
}
{%
   \captionof{figures/fixed_adapt.png}\begin{justify}\vspace{0.25 mm} \textbf{Figure 4:} Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is cost-free (A, $c_{M} = 0$; C, $c_{F} = 0$) or costly (B, $c_{M}=0.02$; D, $c_{F}=0.02$). Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations. Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry. \end{justify}{\t}%
}
\end{adjustwidth}
}

@@

%\begin{small}

\begin{thebibliography}{73}
\providecommand{\natexlab}[1]{#1}

\bibitem[{Ak{\c{c}}ay \& Roughgarden(2007)}]{Akcay2007}
Ak{\c{c}}ay, E. \& Roughgarden, J. 2007.
\newblock {Extra-pair paternity in birds: Review of the genetic benefits}.
\newblock \textit{Evol. Ecol. Res.} \textbf{9}:855--868.

\bibitem[{Ala-Honkola \textit{et~al.}(2011)Ala-Honkola, Manier, L{\"{u}}pold, and
  Pitnick}]{Ala-Honkola2011}
Ala-Honkola, O., Manier, M.~K., L{\"{u}}pold S. \& Pitnick, S. 2011.
\newblock {No evidence for postcopulatory inbreeding avoidance in \textit{Drosophila
  melanogaster}}.
\newblock \textit{Evolution} \textbf{65}:2699--2705.

\bibitem[{Arct \textit{et~al.}(2015)Arct, Drobniak, \& Cicho}]{Arct2015}
Arct, A., Drobniak, S.~M. \& Cicho, M. 2015.
\newblock {Genetic similarity between mates predicts extrapair paternity--a
  meta-analysis of bird studies}.
\newblock \textit{Behav. Ecol.} \textbf{26}:959--968.

\bibitem[{Arnqvist \& Rowe(2005)}]{Arnqvist2005a}
Arnqvist, G. \& Rowe, L. 2005.
\newblock {\textit{Sexual Conflict}}.
\newblock Princeton University Press, Princeton, New Jersey.

\bibitem[{Atamas \& Bell(2009)}]{Atamas2009}
Atamas, S.~P. \& Bell, J. 2009.
\newblock {Degeneracy-driven self-structuring dynamics in selective
  repertoires}.
\newblock \textit{Bull. Math. Biol.} \textbf{71}:1349--1365.

\bibitem[{Bateson(1983)}]{Bateson1983}
Bateson, P. 1983.
\newblock {Optimal outbreeding}.
\newblock Pages 257--277 \emph{in} \textit{Mate Choice}. University Press, Cambridge,
  Cambridge.

\bibitem[{Bocedi \& Reid(2014)}]{Bocedi2014}
Bocedi, G. \& Reid, J.~M. 2014.
\newblock {Evolution of female multiple mating: a quantitative model of the
  ``sexually-selected sperm'' hypothesis}.
\newblock \textit{Evolution} \textbf{69}:39--58.

\bibitem[{Bretman \textit{et~al.}(2009)Bretman, Newcombe, \& Tregenza}]{Bretman2009}
Bretman, A., Newcombe, D. \& Tregenza, T. 2009.
\newblock {Promiscuous females avoid inbreeding by controlling sperm storage}.
\newblock \textit{Mol. Ecol.} \textbf{18}:3340--3345.

\bibitem[{Bussi{\'{e}}re \textit{et~al.}(2006)Bussi{\'{e}}re, Hunt, Jennions, \&
  Brooks}]{Bussiere2006}
Bussi{\'{e}}re, L.~F., Hunt, J., Jennions, M.~D. \& Brooks, R. 2006.
\newblock {Sexual conflict and cryptic female choice in the black field
  cricket, \textit{Teleogryllus commodus}}.
\newblock \textit{Evolution} \textbf{60}:792--800.

\bibitem[{Charlesworth \& Charlesworth(1999)}]{Charlesworth1999}
Charlesworth, B. \& Charlesworth, D. 1999.
\newblock {The genetic basis of inbreeding depression}.
\newblock \textit{Genet. Res.} \textbf{74}:329--340.

\bibitem[{Charlesworth \& Willis(2009)}]{Charlesworth2009}
Charlesworth, D. \& Willis, J.~H. 2009.
\newblock {The genetics of inbreeding depression}.
\newblock \textit{Nat. Rev. Genet.} \textbf{10}:783--796.

\bibitem[{Daniel \& Rodd(2015)}]{Daniel2015}
Daniel, M.~J. \& Rodd, F.~H. 2015.
\newblock {Female guppies can recognize kin but only avoid incest when
  previously mated}.
\newblock \textit{Behav. Ecol.} \textbf{27}:55--61.

\bibitem[{Duthie \textit{et~al.}(2016)Duthie, Bocedi, \& Reid}]{Duthie}
Duthie, A.~B., Bocedi G. \& Reid, J.~M. 2016.
\newblock {When does female multiple mating evolve to adjust inbreeding?
  Effects of inbreeding depression, direct costs, mating constraints, and
  polyandry as a threshold trait}.
\newblock \textit{Evolution} \textbf{70}:1927--1943.

\bibitem[{Duthie \& Reid(2015)}]{Duthie2015a}
Duthie, A.~B. \& Reid, J.~M. 2015.
\newblock {What happens after inbreeding avoidance? Inbreeding by rejected
  relatives and the inclusive fitness benefit of inbreeding avoidance}.
\newblock \textit{PLoS One} \textbf{10}:e0125140.

\bibitem[{Duthie \& Reid(2016)}]{Duthie2016a}
Duthie, A.~B. \& Reid, J.~M. 2016.
\newblock {Evolution of inbreeding avoidance and inbreeding preference through
  mate choice among interacting relatives}.
\newblock \textit{Am. Nat.} \textbf{188}:651--667.

\bibitem[{Edelman \& Gally(2001)}]{Edelman2001}
Edelman, G.~M. \& Gally, J.~A. 2001.
\newblock {Degeneracy and complexity in biological systems}.
\newblock \textit{Proc. Natl. Acad. Sci. USA} \textbf{98}:13763--13768.

\bibitem[{Firman \& Simmons(2008)}]{Firman2008}
Firman, R.~C. \& Simmons, L.~W. 2008.
\newblock {Polyandry facilitates postcopulatory inbreeding avoidance in house
  mice}.
\newblock \textit{Evolution} \textbf{62}:603--611.

\bibitem[{Firman \& Simmons(2015)}]{Firman2015}
Firman, R.~C. \& Simmons, L.~W. 2015.
\newblock {Gametic interactions promote inbreeding avoidance in house mice}.
\newblock \textit{Ecol. Lett.} \textbf{18}:937--943.

\bibitem[{Fischer \textit{et~al.}(2015)Fischer, Karl, Heuskin, Janowitz, \&
  D{\"{o}}tterl}]{Fischer2015}
Fischer, K., Karl, I., Heuskin, S., Janowitz, S. \& D{\"{o}}tterl, S. 2015.
\newblock {Kin recognition and inbreeding avoidance in a butterfly}.
\newblock \textit{Ethology} \textbf{121}:977--984.

\bibitem[{Fitzpatrick \& Evans(2014)}]{Fitzpatrick2014b}
Fitzpatrick, J.~L. \& Evans, J.~P. 2014.
\newblock {Postcopulatory inbreeding avoidance in guppies}.
\newblock \textit{J. Evol. Biol.} \textbf{27}:2585--2594.

\bibitem[{Foerster \textit{et~al.}(2003)Foerster, Delhey, Johnsen, Lifjeld, \&
  Kempenaers}]{Foerster2003}
Foerster, K., Delhey K., Johnsen, A., Lifjeld, J.~T. \& Kempenaers B. 2003.
\newblock {Females increase offspring heterozygosity and fitness through
  extra-pair matings}.
\newblock \textit{Nature} \textbf{425}:714--717.

\bibitem[{Gardner \& Kalinka(2006)}]{Gardner2006}
Gardner, A. \& Kalinka, A.~T. 2006.
\newblock {Recombination and the evolution of mutational robustness}.
\newblock \textit{J. Theor. Biol.} \textbf{241}:707--715.

\bibitem[{Gasparini \& Pilastro(2011)}]{Gasparini2011}
Gasparini, C. \& Pilastro, A. 2011.
\newblock {Cryptic female preference for genetically unrelated males is
  mediated by ovarian fluid in the guppy.}
\newblock \textit{Proc. Biol. Sci.} \textbf{278}:2495--2501.

\bibitem[{Greeff \textit{et~al.}(2009)Greeff, Vuuren, Kryger \& Moore}]{Greeff2009}
Greeff, J.~M., Jansen van Vuuren, G.~J., Kryger, P. \& Moore, J.~C. 2009.
\newblock {Outbreeding and possibly inbreeding depression in a pollinating fig
  wasp with a mixed mating system}.
\newblock \textit{Heredity} \textbf{102}:349--356.

\bibitem[{Guillaume \& Perrin(2009)}]{Guillaume2009}
Guillaume, F. \& Perrin, N. 2009.
\newblock {Inbreeding load, bet hedging, and the evolution of sex-biased
  dispersal.}
\newblock \textit{Am. Nat.} \textbf{173}:536--541.

\bibitem[{Jennions \& Petrie(2000)}]{Jennions2000}
Jennions, M.~D. \& Petrie, M. 2000.
\newblock {Why do females mate multiply? A review of the genetic benefits}.
\newblock \textit{Biol. Rev. Camb. Philos. Soc.} \textbf{75}:21--64.

\bibitem[{Keller \& Waller(2002)}]{Keller2002}
Keller, L.~F. \& Waller,  D.~M. 2002.
\newblock {Inbreeding effects in wild populations}.
\newblock \textit{Trends Ecol. Evol.} \textbf{17}:19--23.

\bibitem[{Kimura(1965)}]{Kimura1965}
Kimura, M. 1965.
\newblock {A stochastic model concerning the maintenance of genetic variability
  in quantitative characters}.
\newblock \textit{Proc. Natl. Acad. Sci. USA} \textbf{54}:731--736.

\bibitem[{Kingma \textit{et~al.}(2013)Kingma, Hall \& Peters}]{Kingma2013}
Kingma, S.~A., Hall, M.~L. \& Peters A. 2013.
\newblock {Breeding synchronization facilitates extrapair mating for inbreeding
  avoidance}.
\newblock \textit{Behav. Ecol.} \textbf{24}:1390--1397.

\bibitem[{Koga \textit{et~al.}(1998)Koga, Backwell, Jennions \& Christy}]{Koga1998}
Koga, T., Backwell, P.~R.~Y., Jennions, M.~D. \& Christy J.~H. 1998.
\newblock {Elevated predation risk changes mating behaviour and courtship in a
  fiddler crab}.
\newblock \textit{Proc. Biol. Sci.} \textbf{265}:1385--1390.

\bibitem[{Kokko \textit{et~al.}(2003)Kokko, Brooks, Jennions \& Morley}]{Kokko2003}
Kokko, H., Brooks R., Jennions M.~D. \& Morley J. 2003.
\newblock {The evolution of mate choice and mating biases.}
\newblock \textit{Proc. Biol. Sci.} \textbf{270}:653--664.

\bibitem[{Kokko \& Mappes(2013)}]{Kokko2013}
Kokko, H. \& Mappes, J. 2013.
\newblock {Multiple mating by females is a natural outcome of a null model of
  mate encounters}.
\newblock \textit{Entomol. Exp. Appl.} \textbf{146}:26--37.

\bibitem[{Kokko \& Ots(2006)}]{Kokko2006}
Kokko, H., \& Ots, I. 2006.
\newblock {When not to avoid inbreeding}.
\newblock \textit{Evolution} \textbf{60}:467--475.

\bibitem[{Kuriwada \textit{et~al.}(2011)Kuriwada, Kumano, Shiromoto \&
  Haraguchi}]{Kuriwada2011}
Kuriwada, T., Kumano, N., Shiromoto, K. \& Haraguchi, D. 2011.
\newblock {Inbreeding avoidance or tolerance? Comparison of mating behavior
  between mass-reared and wild strains of the sweet potato weevil}.
\newblock \textit{Behav. Ecol. Sociobiol.} \textbf{65}:1483--1489.

\bibitem[{Lande(1976)}]{Lande1976}
Lande, R. 1976.
\newblock {The maintenance of genetic variability by mutation in a polygenic
  character with linked loci}.
\newblock \textit{Genet. Res.} \textbf{36}:221--235.

\bibitem[{Lehtonen \& Kokko(2015)}]{Lehtonen2015}
Lehtonen, J. \& Kokko, H. 2015.
\newblock {Why inclusive fitness can make it adaptive to produce less fit
  extra-pair offspring}.
\newblock \textit{Proc. Biol. Sci.} \textbf{282}:20142716.

\bibitem[{Levin \& Lubchenco(2008)}]{Levin2008}
Levin, S.~A. \& Lubchenco, J. 2008.
\newblock {Resilience, robustness, and marine ecosystem-based management}
\newblock \textit{BioScience} \textbf{58}:27--32.

\bibitem[{Lihoreau \textit{et~al.}(2007)Lihoreau, Zimmer \& Rivault}]{Lihoreau2007}
Lihoreau, M., Zimmer, C. \& Rivault, C. 2007.
\newblock {Kin recognition and incest avoidance in a group-living insect}.
\newblock \textit{Behav. Ecol.} \textbf{18}:880--887.

\bibitem[{Liu \textit{et~al.}(2014)Liu, Tu, He, Chen \& Xue}]{Liu2014}
Liu, X., Tu, X., He, H., Chen, C. \& Xue, F. 2014.
\newblock {Evidence for inbreeding depression and pre-copulatory, but not post
  copulatory inbreeding avoidance in the cabbage beetle \textit{Colaphellus bowringi}.}
\newblock \textit{PloS one} \textbf{9}:e94389.

\bibitem[{Lynch \& Walsh(1998)}]{Lynch1998}
Lynch, M. \& Walsh, B. 1998.
\newblock {\textit{Genetics and Analysis of Quantitative Traits}}.
\newblock Sinauer, Sunderland.

\bibitem[{Metzger \textit{et~al.}(2010{\natexlab{\emph{a}}})Metzger, Bernstein,
  Hoffmeister \& Desouhant}]{Metzger2010}
Metzger, M., Bernstein, C., Hoffmeister, T.~S. \& Desouhant, E.
  2010{\natexlab{\emph{a}}}.
\newblock {Does kin recognition and sib-mating avoidance limit the risk of
  genetic incompatibility in a parasitic wasp?}
\newblock \textit{PLoS One} \textbf{5}:1--6.

\bibitem[{Metzger \textit{et~al.}(2010{\natexlab{\emph{b}}})Metzger, Fischbein, Auguste,
  Fauvergue, Bernstein \& Desouhant}]{Metzger2010a}
Metzger, M., Fischbein, D., Auguste, A., Fauvergue, X., Bernstein, C., \&
  Desouhant, E. 2010{\natexlab{\emph{b}}}.
\newblock {Synergy in information use for mate finding: Demonstration in a
  parasitoid wasp}.
\newblock \textit{Anim. Behav.} 79:1307--1315.

\bibitem[{Mills \& Smouse(1994)}]{Mills1994}
Mills, L.~S. \& Smouse, P.~E. 1994.
\newblock {Demographic consequences of inbreeding in remnant populations}.
\newblock \textit{Am. Nat.} \textbf{144}:412--431.

\bibitem[{Morton et~al.(1956)Morton, Crow \& Muller}]{Morton1956}
Morton, N.~E., Crow, J.~F., \& Muller, H.~J. 1956.
\newblock {An estimate of the mutational damage in man from data on
  consanguineous marriages}.
\newblock \textit{Proc. Natl. Acad. Sci. USA} \textbf{42}:855--863.

\bibitem[{Nowak \textit{et~al.}(1997)Nowak, Boerlijst, Cooke, \& {Maynard
  Smith}}]{Nowak1997}
Nowak, M.~A., Boerlijst, M.~C., Cooke, J. \& {Maynard Smith}, J. 1997.
\newblock {Evolution of genetic redundancy}.
\newblock \textit{Nature} \textbf{388}:167--171.

\bibitem[{Park \& Friston(2013)}]{Park2013}
Park, H.~J. \& Friston, K.~J. 2013.
\newblock {Structural and functional brain networks: from connections to
  cognition.}
\newblock \textit{Science} \textbf{342}:1238411.

\bibitem[{Parker(1979)}]{Parker1979}
Parker, G.~A. 1979.
\newblock {Sexual selection and sexual conflict}.
\newblock Pages 123--166 \emph{in} M.~S. Blum \& N.~A. Blum, eds. \textit{Sexual
  selection and reproductive competition in insects}. Academic Press, Inc, New
  York.

\bibitem[{Parker(2006)}]{Parker2006}
Parker, G.~A. 2006.
\newblock {Sexual conflict over mating and fertilization: an overview}.
\newblock \textit{Phil. Trans. R. Soc. Lond. B Biol. Sci.} \textbf{361}:235--259.

\bibitem[{Pizzari \textit{et~al.}(2004)Pizzari, L{\o}vlie, \& Cornwallis}]{Pizzari2004}
Pizzari, T., L{\o}vlie, H. \& Cornwallis, C.~K. 2004.
\newblock {Sex-specific, counteracting responses to inbreeding in a bird}.
\newblock \textit{Proc. Biol. Sci.} \textbf{271}:2115--2121.

\bibitem[{Pomiankowski(1987)}]{Pomiankowski1987}
Pomiankowski, A. 1987.
\newblock {The costs of choice in sexual selection}.
\newblock \textit{J. Theor. Biol.} \textbf{128}:195--218.

\bibitem[{Potts \textit{et~al.}(1991)Potts, Manning \& Wakeland}]{Potts1991}
Potts, W.~K., Manning, C.~J. \& Wakeland, E.~K. 1991.
\newblock {Mating patterns in seminatural populations of mice influenced by MHC
  genotype}.
\newblock \textit{Nature} \textbf{352}:619--621.

\bibitem[{Price \& Friston(2002)}]{Price2002}
Price, C.~J. \& Friston, K.~J. 2002.
\newblock {Degeneracy and cognitive anatomy}.
\newblock \textit{Trends Cogn. Sci.} \textbf{6}:416--421.

\bibitem[{Pusey \& Wolf(1996)}]{Pusey1996}
Pusey, A., \& Wolf, M. 1996.
\newblock {Inbreeding avoidance in animals}.
\newblock \textit{Trends Ecol. Evol.} \textbf{5347}:298--301.

\bibitem[{Reeve(2000)}]{Reeve2000}
Reeve, J.~P. 2000.
\newblock {Predicting long-term response to selection}.
\newblock \textit{Genet. Res.} \textbf{75}:83--94.

\bibitem[{Reid(2015)}]{Reid2015a}
Reid, J.~M. 2015.
\newblock {What can we really say about relatedness and extrapair paternity: a
  comment on Arct \textit{et al}}.
\newblock \textit{Behav. Ecol.} \textbf{26}:969--970.

\bibitem[{Reid \textit{et~al.}(2015{\natexlab{\emph{a}}})Reid, Arcese, Keller, Germain,
  Duthie, Losdat, Wolak \& Nietlisbach}]{Reid2014}
Reid, J.~M., Arcese, P., Keller, L.~F., Germain, R.~R., Duthie, A.~B., Losdat, S.,
  Wolak, M.~E. \& Nietlisbach, P. 2015{\natexlab{\emph{a}}}.
\newblock {Quantifying inbreeding avoidance through extra-pair reproduction}.
\newblock \textit{Evolution} \textbf{69}:59--74.

\bibitem[{Reid \textit{et~al.}(2015{\natexlab{\emph{b}}})Reid, Duthie, Wolak \&
  Arcese}]{Reid2015}
Reid, J.~M., Duthie, A.~B., Wolak, M.~E. \& Arcese, P.
  2015{\natexlab{\emph{b}}}.
\newblock {Demographic mechanisms of inbreeding adjustment through extra-pair
  reproduction}.
\newblock \textit{J. Anim. Ecol.} \textbf{84}:1029--1040.

\bibitem[{Roberts \textit{et~al.}(2015)Roberts, Evison, Baer \& Hughes}]{Roberts2015a}
Roberts, K.~E., Evison, S.~E.~F., Baer, B. \& Hughes, W.~O.~H. 2015.
\newblock {The cost of promiscuity: sexual transmission of \textit{Nosema
  microsporidian} parasites in polyandrous honey bees}.
\newblock \textit{Sci. Rep.} \textbf{5}:10982.

\bibitem[{Roff(1996)}]{Roff1996}
Roff, D.~A. 1996.
\newblock {The evolution of threshold traits in animals}.
\newblock \textit{Q. Rev. Biol.} \textbf{71}:3--35.

\bibitem[{Roff(1998)}]{Roff1998}
Roff, D.~A. 1998.
\newblock {Evolution of threshold traits: the balance between directional
  selection, drift and mutation}.
\newblock \textit{Heredity} \textbf{80}:25--32.

\bibitem[{Ronkainen \& Ylonen(1994)}]{Ronkainen1994}
Ronkainen, H. \& Ylonen, H. 1994.
\newblock {Behaviour of cyclic bank voles under risk of mustelid predation: Do
  females avoid copulations?}
\newblock \textit{Oecologia} \textbf{97}:377--381.

\bibitem[{Rowe(1988)}]{Rowe1988}
Rowe, L. 1988.
\newblock {Cost of mating for female insects: risk of predation in \textit{Photinus
  collustrans} (Coleoptera: Lampyridae)}.
\newblock \textit{Am. Nat.} \textbf{121}:139--142.

\bibitem[{Rowe \textit{et~al.}(1994)Rowe, Arnqvist, Sih \& Krupa}]{Rowe1994}
Rowe, L., Arnqvist, G., Sih, A. \& Krupa, J.~J. 1994.
\newblock {Sexual conflict and the evolutionary ecology of mating patterns:
  water striders as a model system}.
\newblock \textit{Trends Ecol. Evol.} \textbf{9}:289--293.

\bibitem[{Simmons \textit{et~al.}(2006)Simmons, Beveridge, Wedell \&
  Tregenza}]{Simmons2006}
Simmons, L.~W., Beveridge, M., Wedell, N. \& Tregenza, T. 2006.
\newblock {Postcopulatory inbreeding avoidance by female crickets only revealed
  by molecular markers}.
\newblock \textit{Mol. Ecol.} \textbf{15}:3817--3824.

\bibitem[{Suraci \textit{et~al.}(2017)Suraci, Clinchy \& Zanette}]{Suraci2017}
Suraci, J.~P., Clinchy, M. \& Zanette, L.~Y. 2017.
\newblock {Do large carnivores and mesocarnivores have redundant impacts on
  intertidal prey?}
\newblock \textit{PLoS One} \textbf{12}:e0170255.

\bibitem[{Szulkin \textit{et~al.}(2013)Szulkin, Stopher, Pemberton \&
  Reid}]{Szulkin2012}
Szulkin, M., Stopher, K.~V., Pemberton, J.~M. \& Reid, J.~M. 2013.
\newblock {Inbreeding avoidance, tolerance, or preference in animals?}
\newblock \textit{Trends Ecol. Evol.} \textbf{28}:205--211.

\bibitem[{Tan \textit{et~al.}(2012)Tan, L{\o}vlie, Pizzari \& Wigby}]{Tan2012}
Tan, C. K.~W., L{\o}vlie, H., Pizzari, T. \& Wigby, S. 2012.
\newblock {No evidence for precopulatory inbreeding avoidance in \textit{Drosophila
  melanogaster}}.
\newblock \textit{Anim. Behav.} \textbf{83}:1433--1441.

\bibitem[{Tregenza \& Wedell(2002)}]{Tregenza2002}
Tregenza, T. \& Wedell, N. 2002.
\newblock {Polyandrous females avoid costs of inbreeding}.
\newblock \textit{Nature} \textbf{415}:71--73.

\bibitem[{Tuni \textit{et~al.}(2013)Tuni, Beveridge \& Simmons}]{Tuni2013}
Tuni, C., Beveridge, M. \& Simmons, L.~W. 2013.
\newblock {Female crickets assess relatedness during mate guarding and bias
  storage of sperm towards unrelated males}.
\newblock \textit{J. Evol. Biol.} \textbf{26}:1261--1268.

\bibitem[{Varian-Ramos \& Webster(2012)}]{Varian-Ramos2012}
Varian-Ramos, C.~W. \& Webster, M.~S. 2012.
\newblock {Extrapair copulations reduce inbreeding for female red-backed
  fairy-wrens, \textit{Malurus melanocephalus}}.
\newblock \textit{Anim. Behav.} \textbf{83}:857--864.

\bibitem[{Whitacre \& Bender(2010)}]{Whitacre2010}
Whitacre, J. \& Bender, A. 2010.
\newblock {Degeneracy: A design principle for achieving robustness and
  evolvability}.
\newblock \textit{J. Theor Biol.} \textbf{263}:143--153.

\bibitem[{Whitacre(2010)}]{Whitacre2010a}
Whitacre, J.~M. 2010.
\newblock {Degeneracy: a link between evolvability, robustness and complexity
  in biological systems}.
\newblock \textit{Theor. Biol. Med. Model.} \textbf{7}:6.

\bibitem[{Zeh \& Zeh(1997)}]{Zeh1997}
Zeh, J.~A. \& Zeh, D.~W. 1997.
\newblock {The evolution of polyandry II: post-copulatory defenses against
  genetic incompatibility}.
\newblock \textit{Proc. Biol. Sci.} \textbf{264}:69--75.

\end{thebibliography}

%\end{small}
